\textsc{\wobble: a data-driven method for precision radial velocities}

### 2018-11-28 paper/paper.tex
hessian

The stellar spectrum contribution is:
\begin{equation}
y_{n}^\star = P(v_{obs, n}) \mu_{\star},
\end{equation}
where $\mu_{\star}$ is a spectral template with length $M'$ corresponding to
the length of an arbitrarily-chosen wavelength grid of control points, and
$P$ is a linear operator which applies a Doppler shift by velocity $v_n$ and
interpolates $\mu_\star$ into the observatory rest frame.
\todo{MB -- feel free to cut this:} $P$ could be represented as a rectangular
$M \times M'$ sparse matrix, but the dot product can be implemented
efficiently using linear interpolation instead of instantiating the full matrix.
Because we work in log-wavelength space, the Doppler shift due to velocity $v$ is simply an additive term:
\begin{equation}
 \ln \lambda(v) = \ln \lambda_{0} + \frac{1}{2} \ln \left(\frac{1 - v/c}{1 + v/c}\right).
\end{equation}
The $P$ operator adds this term to the $M'$-length wavelength grid for the template spectrum before linearly interpolating the template to the $M$-length data space.

@@

We set regularization amplitudes for \wobble using a cross-validation scheme.
In brief, we set aside 12.5\% of the total epochs as a validation set and, using some value of $\lambda$, run the model optimization on the remaining epochs (the training set).
The resulting best-fit spectral templates and basis vectors are taken as fixed and the time-dependent terms only (\RVs and basis weights) are optimized for the validation epochs.
The $\chi^2$ for the validation epochs can then be adopted as a goodness-of-fit measurement for the $\lambda$ value, and the procedure is repeated for different $\lambda$s to choose the best regularization amplitude.
Because we have multiple regularization terms and multiple amplitudes to set, we begin by hand-setting all amplitudes to a reasonable starting guess and optimize each amplitude sequentially with cross-validation.

@@

The inverse variance uncertainty on the parameters is calculated as the Hessian, or the second derivative of the likelihood with respect to each parameter. \todo{(DFM: help me rephrase if needed?)}

>>>>

The stellar spectrum contribution is:
\begin{equation}
y_{n}^\star = P(v_{obs, n}) \mu_{\star},
\end{equation}
where $\mu_{\star}$ is a spectral template with length $M'$ corresponding to
the length of an arbitrarily-chosen wavelength grid of control points, and
$P$ is a linear operator which applies a Doppler shift by velocity $v_n$ and
interpolates $\mu_\star$ into the observatory rest frame.
Because we work in log-wavelength space, the Doppler shift due to velocity $v$ is simply an additive term:
\begin{equation}
 \ln \lambda(v) = \ln \lambda_{0} + \frac{1}{2} \ln \left(\frac{1 - v/c}{1 + v/c}\right).
\end{equation}
The $P$ operator adds this term to the $M'$-length wavelength grid for the template spectrum before linearly interpolating the template to the $M$-length data space.
\todo{MB -- feel free to cut this:} $P$ could be represented as a rectangular
$M \times M'$ sparse matrix, but the dot product can be implemented
efficiently using linear interpolation instead of instantiating the full matrix.

@@

We set regularization amplitudes for \wobble using a cross-validation scheme.
In brief, we randomly select 12.5\% of the total epochs to set aside as a validation set and, using some value of $\lambda$, run the model optimization on the remaining epochs (the training set).
The resulting best-fit spectral templates and basis vectors are taken as fixed and the time-dependent terms only (\RVs and basis weights) are optimized for the validation epochs.
The $\chi^2$ for the validation epochs can then be adopted as a goodness-of-fit measurement for the $\lambda$ value, and the procedure is repeated for different $\lambda$s to choose the best regularization amplitude.
Because we have multiple regularization terms and multiple amplitudes to set, we begin by hand-setting all amplitudes to a reasonable starting guess and optimize each amplitude sequentially with cross-validation.

@@

After convergence, we estimate the uncertainties on the parameters by
approximating the likelihood function near its maximum as Gaussian where the
covariance matrix is the negative inverse Hessian (or second derivative
matrix) of the log likelihood function with respect to the parameters.
